\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-04 paper/main.tex
.

The baseline predictor shows significantly\todo{p-val} higher
performance than a random classifier on both datasets, with better
results on the Yamanishi benchmark.

>>>>

The baseline\todo{What is this? The naive one?} predictor shows significantly\todo{p-val} higher
performance than a random classifier on both datasets, with better
results on the Yamanishi benchmark.
